---
title: "Default colours along a variable in INBOtheme"
author: "Thierry Onkelinx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Default colours along a variable in INBOtheme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

Some themes impact the scales when using a colour or fill along a variable.
This vignette focusses on the different styles of colour scales.
The fill scales uses the same gradients.
To keep the vignette small, we only give examples with different colours.
We illustrate the other effects of the themes in `vignette("colour", package = "INBOtheme")`, again to keep the size of the vignettes to a minimum.
Note that you need to use the appropriate scale provided by `INBOtheme` in case of a gradient along a continuous variable.

```{r knitr, include = FALSE}
library(knitr)
opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE, dev = "png",
  dpi = ifelse(opts_knit$get("rmarkdown.pandoc.to") == "latex", 300, 72)
)
```

```{r initialise}
library(ggplot2)
library(INBOtheme)
```

# Default: `theme_inbo()`

```{r inbo-plots, results = "asis", echo = FALSE}
base_size <- ifelse(opts_knit$get("rmarkdown.pandoc.to") == "latex", 7, 12)
theme_set(theme_inbo(base_size = base_size))
rmd <- knit_expand("child/_colour_test_figures.Rmd", theme = "inbo")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

# `theme_vlaanderen2015()`

```{r set_theme_vlaanderen2015, echo = FALSE}
theme_set(theme_vlaanderen2015(base_size = base_size))
```

```{r vlaanderen-plots, results = "asis", echo = FALSE}
rmd <- knit_expand("child/_colour_test_figures.Rmd", theme = "vlaanderen")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

# `theme_elsevier()`

```{r set_theme_elsevier, echo = FALSE}
theme_set(theme_elsevier(base_size = base_size))
```

```{r elsevier-plots, results = "asis", echo = FALSE}
rmd <- knit_expand("child/_colour_test_figures.Rmd", theme = "elsevier")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```
