---
title: "Available colour palettes in INBOtheme"
author: "Thierry Onkelinx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Available colour palettes in INBOtheme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette demonstrates the available colour palettes in the `INBOtheme` package.
We show the palette as a plot with numbered rectangles.
The number indicates the order in the palette.


```{r knitr, include = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE, fig.width  = 7.2,
  fig.height = 5
)
```

```{r initialise, echo = TRUE}
library(INBOtheme)
library(colorblindr)
```

# Palettes

## `inbo_palette`

```{r inbo_palette}
demo_palette(inbo_palette())
```

## `vlaanderen_palette`

```{r vlaanderen-palette}
demo_palette(vlaanderen_palette())
```

## `traffic_palette`

Note that the `traffic_palette()` has a variable number of colours.
It starts from a dark red colour and changes into a light green.
Going gradually from dark to light makes this palette readable for colour blind people.

```{r traffic_palette_9, fig.cap = "`traffic_palette()` with 9 levels."}
demo_palette(traffic_palette(9))
```

```{r traffic_palette_3, fig.cap = "`traffic_palette()` with 3 levels."}
demo_palette(traffic_palette(3))
```

# Simulate effect of colour blindness on the perception of palettes

## `inbo_palette`

```{r inbo-palette-deutan, fig.cap = "Simulation of deutan model of colorblindness."}
demo_palette(deutan(inbo_palette()))
```

```{r inbo-palette-protan, fig.cap = "Simulation of protan model of colorblindness."}
demo_palette(protan(inbo_palette()))
```

```{r inbo-palette-tritan, fig.cap = "Simulation of tritan model of colorblindness."}
demo_palette(tritan(inbo_palette()))
```

```{r inbo-palette-gray, fig.cap = "Desaturated colours."}
demo_palette(desaturate(inbo_palette()))
```

## `vlaanderen_palette`

```{r vlaanderen-palette-deutan, fig.cap = "Simulation of deutan model of colorblindness."}
demo_palette(deutan(vlaanderen_palette()))
```

```{r vlaanderen-palette-protan, fig.cap = "Simulation of protan model of colorblindness."}
demo_palette(protan(vlaanderen_palette()))
```

```{r vlaanderen-palette-tritan, fig.cap = "Simulation of tritan model of colorblindness."}
demo_palette(tritan(vlaanderen_palette()))
```

```{r vlaanderen-palette-gray, fig.cap = "Desaturated colours."}
demo_palette(desaturate(vlaanderen_palette()))
```

## `traffic_palette`

```{r traffic-palette-deutan, fig.cap = "Simulation of deutan model of colorblindness."}
demo_palette(deutan(traffic_palette(9)))
```

```{r traffic-palette-protan, fig.cap = "Simulation of protan model of colorblindness."}
demo_palette(protan(traffic_palette(9)))
```

```{r traffic-palette-tritan, fig.cap = "Simulation of tritan model of colorblindness."}
demo_palette(tritan(traffic_palette(9)))
```

```{r traffic-palette-gray, fig.cap = "Desaturated colours."}
demo_palette(desaturate(traffic_palette(9)))
```
