---
title: "Available themes in INBOtheme"
author: "Thierry Onkelinx"
output:
  rmarkdown::html_vignette:
    fig_width: 7.2
    fig_height: 5
  rmarkdown::pdf_document:
    extra_dependencies: placeins
    fig_width: 5
    fig_height: 3
vignette: >
  %\VignetteIndexEntry{Available themes in INBOtheme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette gives a short introduction on the `INBOtheme` package.
The `INBOtheme` package provides a few themes for `ggplot2`.
This vignette demonstrates the look and feel of the themes by showing several plots.
Many of the figures in this vignettes are taken from the examples from the `ggplot2` package.

The `ggplot2` package must be loaded prior to `INBOtheme`.

```{r knitr, include = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE
)
```

```{r initialise, echo = TRUE}
library(ggplot2)
library(INBOtheme)
library(colorblindr)
```

```{r create_simple_dataset}
pp <- function(n) {
  df <- expand.grid(
    x = seq_len(n),
    y = seq_len(n)
  )
  df$z <- df$x + df$y
  df
}

df <- data.frame(
  trt = factor(c(1, 1, 2, 2)),
  resp = c(1, 5, 3, 4),
  group = factor(c(1, 2, 1, 2)),
  se = c(0.1, 0.3, 0.3, 0.2)
)

testgrid <- expand.grid(x = 1:4, y = 1:4)
testgrid$z <- factor((testgrid$x - 1) * 4 + testgrid$y)
```

```{r default_theme}
update_geom_defaults("text", list(size = 2.5))
```

# Default: `theme_inbo()`

## `theme_inbo()` with default background

```{r set_theme_inbo, echo = TRUE}
theme_set(theme_inbo())
switch_colour(inbo_steun_blauw)
```

```{r inbo-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "inbo")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

## `theme_inbo()` with transparent background

```{r set_theme_inbo_transparant, echo = TRUE}
theme_set(theme_inbo(transparent = TRUE))
switch_colour(inbo_steun_blauw)
```

```{r inbo-transparant-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "inbo-tr")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

# `theme_vlaanderen2015()`

## `theme_vlaanderen2015()` with default background

```{r set_theme_vlaanderen2015, echo = TRUE}
theme_set(theme_vlaanderen2015())
switch_colour(vl_darkyellow)
```

```{r vlaanderen-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "vlaanderen")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

## `theme_vlaanderen2015()` with transparent background

```{r set_theme_vlaanderen2015_transparant, echo = TRUE}
theme_set(theme_vlaanderen2015(transparent = TRUE))
switch_colour(vl_darkyellow)
```

```{r vlaanderen-transparant-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "vlaanderen-tr")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

# `theme_elsevier()`

```{r set_theme_elsevier, echo = TRUE}
theme_set(theme_elsevier(12))
switch_colour("black")
```

```{r elsevier-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "elsevier")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```
