---
title: "Available themes in INBOtheme"
author: "Thierry Onkelinx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Available themes in INBOtheme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette focuses on the available `ggplot2` themes in `INBOtheme`.
They mainly control the looks of the axes, background, legend, ...
Some themes also impact the schemes when using a colour or fill along a variable.
We illustrate that in `vignette("colour", package = "INBOtheme")`.

## Important

The `ggplot2` package must be loaded prior to `INBOtheme`.
Loading `INBOtheme` sets `inbo_theme()` as default theme and `inbo_steun_blauw` as default colour for the `geoms`.
Note how we use `theme_set()` and `switch_colour()`.
This applies the theme and colour to all subsequent plots without the need to change the `ggplot2` code.

### Using the default theme from `INBOtheme`

Add the following code after loading the `ggplot2` or `tidyverse` package and before creating the `ggplot2` plots.

```{r eval = FALSE, echo = TRUE}
library(INBOtheme)
```

In case you need to change the default font size or background add the code below after loading the package.

```{r eval = FALSE, echo = TRUE}
theme_set(theme_inbo(base_size = 12, transparent = FALSE))
```


### Using a non-default theme from `INBOtheme`

Add the following code after loading the `ggplot2` or `tidyverse` package and before creating the `ggplot2` plots.

```{r eval = FALSE, echo = TRUE}
library(INBOtheme)
theme_set(theme_vlaanderen2015(base_size = 12, transparent = FALSE))
switch_colour(vl_darkyellow)
```

```{r eval = FALSE, echo = TRUE}
library(INBOtheme)
theme_set(theme_elsevier(base_size = 12, transparent = FALSE))
switch_colour("black")
```

# Prepare the code and data

```{r knitr, include = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE
)
base_size <- ifelse(opts_knit$get("rmarkdown.pandoc.to") == "latex", 7, 12)
```

```{r initialise, echo = TRUE}
library(ggplot2)
library(INBOtheme)
```

```{r prepare-data, echo = TRUE}
# Prepare the data for the figures
d <- data.frame(
  x = "Sphinx of black quartz, judge my vow",
  y = "Sphinx of\nblack quartz,\njudge my vow"
)
data("esoph")
cancer <- esoph
cancer$Age <- cancer$agegp
cancer$Alcohol <- cancer$alcgp
cancer$Tabacco <- cancer$tobgp
cancer$Proportion <- cancer$ncases / (cancer$ncases + cancer$ncontrols)
```

# Default: `theme_inbo()`

## `theme_inbo()` with default background


```{r set_theme_inbo, echo = TRUE, eval = FALSE}
theme_set(theme_inbo(base_size = 12))
switch_colour(inbo_steun_blauw)
```

```{r set_theme_inbo2, echo = FALSE}
theme_set(theme_inbo(base_size = base_size))
switch_colour(inbo_steun_blauw)
```

```{r inbo-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "inbo")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

## `theme_inbo()` with transparent background

```{r set_theme_inbo_transparant, echo = TRUE, eval = FALSE}
theme_set(theme_inbo(base_size = 12, transparent = TRUE))
switch_colour(inbo_steun_blauw)
```

```{r set_theme_inbo_transparant2, echo = FALSE}
theme_set(theme_inbo(base_size = base_size, transparent = TRUE))
switch_colour(inbo_steun_blauw)
```

```{r inbo-transparant-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "inbo-tr")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

# `theme_vlaanderen2015()`

## `theme_vlaanderen2015()` with default background

```{r set_theme_vlaanderen2015, echo = TRUE, eval = FALSE}
theme_set(theme_vlaanderen2015(base_size = 12))
switch_colour(vl_darkyellow)
```

```{r set_theme_vlaanderen20152, echo = FALSE}
theme_set(theme_vlaanderen2015(base_size = base_size))
switch_colour(vl_darkyellow)
```

```{r vlaanderen-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "vlaanderen")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

## `theme_vlaanderen2015()` with transparent background

```{r set_theme_vlaanderen2015_transparant, echo = TRUE, eval = FALSE}
theme_set(theme_vlaanderen2015(base_size = 12, transparent = TRUE))
switch_colour(vl_darkyellow)
```

```{r set_theme_vlaanderen2015_transparant2, echo = FALSE}
theme_set(theme_vlaanderen2015(base_size = base_size, transparent = TRUE))
switch_colour(vl_darkyellow)
```

```{r vlaanderen-transparant-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "vlaanderen-tr")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```

# `theme_elsevier()`

Note that `theme_elsevier()` uses a base font size of 7.
Use that default when preparing plots for a paper.

```{r set_theme_elsevier, echo = TRUE, eval = FALSE}
theme_set(theme_elsevier(base_size = 12))
switch_colour("black")
```

```{r set_theme_elsevier2, echo = FALSE}
theme_set(theme_elsevier(base_size = base_size))
switch_colour("black")
```

```{r elsevier-plots, results = "asis"}
rmd <- knit_expand("child/_themes_test_figures.Rmd", theme = "elsevier")
md <- knit(text = rmd, quiet = TRUE)
cat(md)
```
