## Continuous variable

```{r {{theme}}-point-gradient, fig.cap = "Coloured along a continuous variable."}
ggplot(diamonds, aes(x = carat, y = depth, colour = price)) +
  geom_point() +
  scale_colour_gradient()
```

\FloatBarrier

```{r {{theme}}-tile-gradient2, fig.cap = "Coloured along a continuous variable using a gradient with midpoint."}
ggplot(diamonds, aes(x = carat, y = depth, colour = price)) +
  geom_point() +
  scale_colour_gradient2(midpoint = 1e4)
```

\FloatBarrier

## Ordinal variable

```{r {{theme}}-histogram-oridinal, fig.cap = "Coloured along an ordinal variable."}
ggplot(diamonds, aes(x = carat, y = depth, colour = cut)) +
  geom_point()
```

\FloatBarrier

## Categorical variable

Here we illustrate figures with a different number of categories.
We choose for scatter plots with random x, y and category.
This is the most difficult situation to distinguish the colours.
Be careful when you use more than 5 colours.

```{r {{theme}}-categorical-2, fig.cap = "Coloured by a two level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:2], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier

```{r {{theme}}-categorical-3, fig.cap = "Coloured by a three level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:3], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier

```{r {{theme}}-categorical-4, fig.cap = "Coloured by a four level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:4], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier

```{r {{theme}}-categorical-5, fig.cap = "Coloured by a five level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:5], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier

```{r {{theme}}-categorical-6, fig.cap = "Coloured by a six level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:6], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier

```{r {{theme}}-categorical-7, fig.cap = "Coloured by a seven level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:7], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier

```{r {{theme}}-categorical-8, fig.cap = "Coloured by an eight level categorical variable."}
data.frame(
  x = runif(1e3), y = runif(1e3),
  category = sample(LETTERS[1:8], 1e3, replace = TRUE)
) |>
  ggplot(aes(x = x, y = y, colour = category)) +
  geom_jitter()
```

\FloatBarrier
